Online {\IterComp}

### 2017-11-16 work.tex
minor fix

    To compute the amount of work associated with each instrumentation probe, we first need to determine how reaching a probe relates with
    executing or not a basic block. Starting from instrumented edges, we use Kirchhoff's first law~\cite{knuth73,ball94} and a post-order
    traversal of the spanning tree to build symbolic expressions of edge frequencies as linear functions of probe counts, as seen in
    Figure~\ref{fig:cfg-example}. This part is similar to how edge and block frequencies are calculated in prior work for basic block
    profiling, with a few key differences:
    (i)   work profiling does not have to store the execution count of each basic block, only the total work which makes it cheaper to profile;
    (ii)  it does not require a post-processing of the recorded profiling for populating the edge flows;
    (iii) the propagation of the edge flows happens in a symbolic fashion during the instrumentation of the code, as depicted in Figure~\ref{fig:cfg-example}.
    This symbolic edge flows are used to derive the frequency expression of the basic blocks, which is then used to derive the amount of work
    recorded by each probe.

>>>>

    To compute the amount of work associated with each instrumentation probe, we first need to determine how reaching a probe relates with
    executing or not a basic block. Starting from instrumented edges, we use Kirchhoff's first law~\cite{knuth73,ball94} and a post-order
    traversal of the spanning tree to build symbolic expressions of edge frequencies as linear functions of probe counts, as seen in
    Figure~\ref{fig:cfg-example}. This part is similar to how edge and block frequencies are calculated in prior work for basic block
    profiling, with a few key differences:
    (i)   work profiling does not have to store the execution count of each basic block, only the total work which makes it cheaper to profile;
    (ii)  it does not require a post-processing of the recorded profiling for populating the edge flows;
    (iii) the propagation of the edge flows happens in a symbolic fashion during the instrumentation of the code, as depicted in Figure~\ref{fig:cfg-example}.
    These symbolic edge flows are used to derive the frequency expressions of the basic blocks, which are then used to derive the amount of work
    recorded by each probe.
